Sketch Recognition and Understanding

### 2009-04-27 draft/SketchMaster.tex

I would like to convey my sincere appreciation and graditude to my supervisors; Dr. Nevin Darwish, Dr. Magdah Fayek and Dr. Samia Mashali. I would also be very gratuful for Dr. Mahmoud Fakhr El Din for his assitance with my thesis. Thanks for all the time devoted in making constructive comments and suggestions for improving this thesis. 
I thank my family and friends for thier moral and support. I specifically thank, dina said, noha mansour and marwah shafee. Thanks, for being always there when I needed you the most. I hope to express my gratiude to all of you for supproting me and praying for me through all these years. 
 %Finally, I am very grateful to my dear parents, my family, and my friends whom I consider
%as my sisters. I would like to thank particularly Radwa Aboudina, Fatma Nada, Maha
%Nabil, Haidi Badr, and Marwa Kamal. Thank you all for being always there when I needed
%you most. Thank you for believing in me and supporting me through all these years. I think
%without your support and your prayers, none of this work would be accomplished.
%ii
 \end{acknowledgments}                                   %

>>>>

I would like to convey my sincere appreciation and gratitude to my supervisors; Dr. Nevin Darwish, Dr. Magdah Fayek and Dr. Samia Mashali. I would also be very grateful for Dr. Mahmoud Fakhr El Din for his assistance with my thesis. Thanks for all the time devoted in making constructive comments and suggestions for improving this thesis.

 I thank my family and friends for their moral and support. I specifically thank, dina said, noha mansour and marwah shafee. Thanks, for being always there when I needed you the most. I hope to express my gratitude to all of you for supporting me and praying for me through all these years.
 %Finally, I am very grateful to my dear parents, my family, and my friends whom I consider
%as my sisters. I would like to thank particularly Radwa Aboudina, Fatma Nada, Maha
%Nabil, Haidi Badr, and Marwa Kamal. Thank you all for being always there when I needed
%you most. Thank you for believing in me and supporting me through all these years. I think
%without your support and your prayers, none of this work would be accomplished.
%ii
 \end{acknowledgments}                                   %
